Numerical trajectory patterns of floating macroalgae

### 2020-12-16 thesis_chapter_3.Rmd
outputs updated

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  html_document:
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  html_document:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---
